Why do people punish? Evidence for a range of strategic concerns

### 2023-12-13 appendix.Rmd
update manuscript

(ref:plotModel1aCaption) *Posterior estimates of the probabilities of following
different punishment strategies from the Bayesian latent state model fitted to
the full dataset without pre-registered exclusions.* The model assumes an 
implementation error rate of 5%. Points represent posterior medians, line ranges 
represent 50% and 95% credible intervals.

@@

(ref:plotAllDems2Caption) *Posterior slopes from models including age, 
socio-economic status, gender, and student status, fitted to the subsetted 
dataset with pre-registered exclusions.* Each row represents a separate model. 
Points represent posterior medians, line ranges represent 95% credible intervals.

@@

(ref:plotAllDems1Caption) *Posterior slopes from models including age, 
socio-economic status, gender, and student status, fitted to the full dataset 
without pre-registered exclusions.* Each row represents a separate model. Points 
represent posterior medians, line ranges represent 95% credible intervals.

@@

(ref:plotAllPers1Caption) *Posterior slopes from models including Big-6 
personality dimensions and Social Value Orientation, fitted to the full dataset 
without pre-registered exclusions.* Each row represents a separate model. Points 
represent posterior medians, line ranges represent 95% credible intervals.

@@

(ref:plotAllPolRel1Caption) *Posterior slopes from models including political 
ideology, views about social inequality, and religiosity, fitted to the full 
dataset without pre-registered exclusions.* Each row represents a separate model 
aside from Social Dominance Orientation and Right Wing Authoritarianism, which 
control for one another within the same model. Points represent posterior 
medians, line ranges represent 95% credible intervals.

@@

(ref:plotAllSliders1Caption) *Posterior slopes from models including 
self-reported strategy usage, fitted to the full dataset without pre-registered 
exclusions.* Each row represents a separate model. Highlighted estimates 
represent combinations where the self-report slider matched the behavioural 
strategy. Each strategy had an associated self-report slider except for the 
competitive strategy. Points represent posterior medians, line ranges represent 
95% credible intervals.

@@

@@

(ref:plotSimCaption) *Results of Bayesian latent state model fitted to simulated
data (n = 100) with known strategy frequencies in the population.* Blue points
represent known strategy frequencies, grey densities represent posterior
estimates of strategy frequencies.

>>>>

(ref:plotModel1aCaption) *Posterior estimates of the probabilities of following
different punishment strategies from the Bayesian latent state model fitted to
the full dataset without pre-registered exclusions.* The model assumes an 
implementation error rate of 5%. Points represent posterior medians, line ranges 
represent 50% and 95% credible intervals. AI = advantageous inequity, DI = 
disadvantageous inequity.

@@

(ref:plotAllDems2Caption) *Posterior slopes from models including age, 
socio-economic status, gender, and student status, fitted to the subsetted 
dataset with pre-registered exclusions.* Each row represents a separate model. 
Points represent posterior medians, line ranges represent 95% credible
intervals. AI = advantageous inequity, DI = disadvantageous inequity.

@@

(ref:plotAllDems1Caption) *Posterior slopes from models including age, 
socio-economic status, gender, and student status, fitted to the full dataset 
without pre-registered exclusions.* Each row represents a separate model. Points 
represent posterior medians, line ranges represent 95% credible intervals. AI = 
advantageous inequity, DI = disadvantageous inequity.

@@

(ref:plotAllPers1Caption) *Posterior slopes from models including Big-6 
personality dimensions and Social Value Orientation, fitted to the full dataset 
without pre-registered exclusions.* Each row represents a separate model. Points 
represent posterior medians, line ranges represent 95% credible intervals. AI = 
advantageous inequity, DI = disadvantageous inequity.

@@

(ref:plotAllPolRel1Caption) *Posterior slopes from models including political 
ideology, views about social inequality, and religiosity, fitted to the full 
dataset without pre-registered exclusions.* Each row represents a separate model 
aside from Social Dominance Orientation and Right Wing Authoritarianism, which 
control for one another within the same model. Points represent posterior 
medians, line ranges represent 95% credible intervals. AI = advantageous 
inequity, DI = disadvantageous inequity.

@@

(ref:plotAllSliders1Caption) *Posterior slopes from models including 
self-reported strategy usage, fitted to the full dataset without pre-registered 
exclusions.* Each row represents a separate model. Highlighted estimates 
represent combinations where the self-report slider matched the behavioural 
strategy. Each strategy had an associated self-report slider except for the 
competitive strategy. Points represent posterior medians, line ranges represent 
95% credible intervals. AI = advantageous inequity, DI = disadvantageous 
inequity.

@@

(ref:plotModel5Caption) *Posterior estimates of the probabilities of following
different punishment strategies from the Bayesian latent state model that
estimates the implementation error rate as a free parameter.* The model
estimated the implementation error rate to be `r printnum(median(error))`
(95% CI [`r printnum(quantile(error, 0.025))`
`r printnum(quantile(error, 0.975))`]). Points represent posterior medians, line 
ranges represent 50% and 95% credible intervals. AI = advantageous inequity, DI
= disadvantageous inequity.

```{r plotModel5, fig.width=7, fig.height=5, fig.cap="(ref:plotModel5Caption)", warning=FALSE}
tar_read(plot5)
```

@@

(ref:plotSimCaption) *Results of Bayesian latent state model fitted to simulated
data (n = 100) with known strategy frequencies in the population.* Blue points
represent known strategy frequencies, grey densities represent posterior
estimates of strategy frequencies. AI = advantageous inequity, DI = 
disadvantageous inequity.
